LaTeX draft for \\"Ancient Greece Yuri Visual Novel"

### 2015-10-04 text/draft.tex
Tying up a missing bad end

>>>>

\gsection{Drunk}

I'm not especially weak to alcohol, but trying to match Antiope cup for cup is not really a good idea. I'm quickly dizzy while she acts more like a soulless machine with each new gulp. I try to speak, but my elocution has been diluted in the wine, as was Antiope's attention.\\

\dcomment{
	Like the "Do nothing ending", with slightly altered text
}
